\ttitle

### 2013-11-01 Chapters/Chapter2.tex
Replace `takes` by `follows`

The widely used \gls{cusum} method by Basseville \etal \cite{basseville1993detection} takes this approach.
It originates from control methods for detection from bench marks.
This method and some derivatiges are discussed and analyzed in section \ref{cusum}.

@@

The density-estimation methods rely on the log-likelihood ratio between \glspl{pdf}.
The method of Camci \cite{camci2010change} takes an other approach within the statistical framework, by using a \gls{svm}.
One problem it tries to overcome is the (claimed) weakness of many methods to detect a decrease in variance.
The method represents the distribution over the data points as a hyper-sphere in a higher dimension using the kernel trick.
A change in the \gls{pdf} is represented by a change in the radius of this sphere.
Section \ref{sec:svm_in_change_detection} discusses the \gls{svm}-methods.
\TODO{Put emphasis that this is the source of inspiration for the chosen method?}

% The final method under consideration, change detection via (intrinsic) dimensionality reduction, takes a different point of view.
% Opposed to the other discussed methods, dimensionality reduction is framed in the MDL (Minimum Description Length) framework.
% It uses the estimated underlying number of parameters of the time series as a model for change detection.
% Section \ref{dim-reduction} discuses this method.

>>>>

The widely used \gls{cusum} method by Basseville \etal \cite{basseville1993detection} follows this approach.
It originates from control methods for detection from bench marks.
This method and some derivatiges are discussed and analyzed in section \ref{cusum}.

@@

The density-estimation methods rely on the log-likelihood ratio between \glspl{pdf}.
The method of Camci \cite{camci2010change} follows an other approach within the statistical framework, by using a \gls{svm}.
One problem it tries to overcome is the (claimed) weakness of many methods to detect a decrease in variance.
The method represents the distribution over the data points as a hyper-sphere in a higher dimension using the kernel trick.
A change in the \gls{pdf} is represented by a change in the radius of this sphere.
Section \ref{sec:svm_in_change_detection} discusses the \gls{svm}-methods.
\TODO{Put emphasis that this is the source of inspiration for the chosen method?}

% The final method under consideration, change detection via (intrinsic) dimensionality reduction, follows a different point of view.
% Opposed to the other discussed methods, dimensionality reduction is framed in the MDL (Minimum Description Length) framework.
% It uses the estimated underlying number of parameters of the time series as a model for change detection.
% Section \ref{dim-reduction} discuses this method.

### 2013-11-01 Chapters/Chapter2/temporal_segmentation.tex
Replace `takes` by `follows`

The time series data from a sensor can be considered as being drawn from a certain stochastic process.
Probabilistic models can be constructed on that signal, yielding in probabilistic and Bayesian based segmentation methods.
The \gls{cusum}-methods takes a statistical approach and relies on the log-likelihood ratio \cite{gustafsson1996marginalized} to measure the difference between two distributions.
To calculate the ratio, the probability density functions need to be calculated.
The method of Kawahara \etal \cite{kawahara2009change} proposes to estimate the ratio of probability densities (known as the \emph{importance}), based on the log likelihood of test samples, directly, without explicit estimation of the densities.
The method by Liu \etal \cite{liu2013change} uses a comparable dissimilarity measure using the \gls{kliep} algorithm.
They claim this results in a robuster approach for real-world scenarios.
Although this is a model-based method, no strong assumptions (parameter settings) are made on the models.

>>>>

The time series data from a sensor can be considered as being drawn from a certain stochastic process.
Probabilistic models can be constructed on that signal, yielding in probabilistic and Bayesian based segmentation methods.
The \gls{cusum}-methods follows a statistical approach and relies on the log-likelihood ratio \cite{gustafsson1996marginalized} to measure the difference between two distributions.
To calculate the ratio, the probability density functions need to be calculated.
The method of Kawahara \etal \cite{kawahara2009change} proposes to estimate the ratio of probability densities (known as the \emph{importance}), based on the log likelihood of test samples, directly, without explicit estimation of the densities.
The method by Liu \etal \cite{liu2013change} uses a comparable dissimilarity measure using the \gls{kliep} algorithm.
They claim this results in a robuster approach for real-world scenarios.
Although this is a model-based method, no strong assumptions (parameter settings) are made on the models.

### 2013-11-01 Chapters/Chapter3/one_class_svm.tex
Replace `takes` by `follows`

\subsection{\acrlong{svdd}}\label{subsec:oc-svm-svdd}
The method introduced by Tax and Duin \cite{tax1999support}, known as \acrlong{svdd}, takes a spherical instead of planar approach.
The boundary, created in feature space $\mathcal{F}$, forms a hypersphere around the (high density region of the) data.
The volume of this hypersphere is minimized to get the smallest enclosing boundary.
The chance of accepting outlier objects is thereby also minimized \cite{tax2003online}.
By allowing outliers using slacks variables, in the same manner as classical \gls{svm} and \gls{nu-svm}, a soft margin is constructed.

>>>>

\subsection{\acrlong{svdd}}\label{subsec:oc-svm-svdd}
The method introduced by Tax and Duin \cite{tax1999support}, known as \acrlong{svdd}, follows a spherical instead of planar approach.
The boundary, created in feature space $\mathcal{F}$, forms a hypersphere around the (high density region of the) data.
The volume of this hypersphere is minimized to get the smallest enclosing boundary.
The chance of accepting outlier objects is thereby also minimized \cite{tax2003online}.
By allowing outliers using slacks variables, in the same manner as classical \gls{svm} and \gls{nu-svm}, a soft margin is constructed.
